Assignment 3

### 2015-02-16 rmtw/a3/latex8.tex
Added RQs

\Section{Purpose of the Study}
The purpose of this study is to explore how changes to software processes are incorporated into a company where differing development paradigms are used. This exploratory study will take place at a large and successful telecommunications company. Much of the qualitative data will originate from current employees via a series of interviews. While the study will only take place at a single location, it will be conducted in such a way that it is applicable to any company willing to partake.

\SubSection{Research Question(s)}
RQ: How is change managed in a company which has a split development strategy (e.g. mdsd+manual)?
SRQ1: How can it be done better blabla?
SRQ2: How can a company determine if a change will conflict with a current paradigm?

@@

@@

\begin{itemize}
\item Create questions for your interviews (include the questions in your report)
\item Discuss validity threats
\item Triangulation = counteract research bias
\item In meth, mention how the interviewees were selected and contacted (you have a gatekeeper which selects the people for you)
\item Mention how many of each role and why each role was included (triangulation)
\item convenience sampling (yo uhave contact at company already and use them) and maximum varation (i aim to have as many as possible)
\item Mention how the company was selected and what the criteria was (there was some lazy w)
\end{itemize}

>>>>

\Section{Purpose of the Study}
The purpose of this case study is to explore how changes to software processes are incorporated into a company where multiple development paradigms are used. The study has been designed for change agents and it has been conducted at the EPG department at Ericsson. At this stage in the research, the central phenomenon being studied, how changes are implemented in companies where more than one development paradigms are used, will be generally defined as implementing change in multi-paradigm environments.

\SubSection{Research Question(s)}
RQ: How is change managed in multi-paradigm environments?
SRQ1: What are the challanges of implementing change in multi-paradigm environments?
SRQ2: How can a company determine if a change will conflict with the currently used development paradigms?
SRQ3: How can an organisation's development paradigm be used as a basis for deciding which changes to adopt?

@@

\begin{itemize}
\item Create questions for your interviews (include the questions in your report)
\item Discuss validity threats
\item Triangulation = counteract research bias
\item In meth, mention how the interviewees were selected and contacted (you have a gatekeeper which selects the people for you)
\item Mention how many of each role and why each role was included (triangulation)
\item convenience sampling (yo uhave contact at company already and use them) and maximum varation (i aim to have as many as possible)
\item Mention how the company was selected and what the criteria was (there was some lazy w)
\item the documents analysis (triangulation) will mostly be used to verify what the change agents say
\end{itemize}

@@
